### 2019-04-15 paper/paper.tex
more content

\subsection{Package Metadata}

@@

Figure 2 [CURRENTLY MISSING][MORE DATA COMMENTARY].

To better visualize the status of inter-package dependencies, we constructed
a directed dependency graph using dependants as out-degrees and
dependencies as in-degrees. Based on this graph, Figure \ref{outDegree}
displays the percentage of packages with various amounts of dependencies. 
[MIGHT NEED TO CHANGE BASED ON DATA: While the average number of dependencies 
of packages continues to increase, the percentage of packages with zero 
to three dependencies has actually increased since the end of the original paper's
reporting period \cite{Wittern:2016}. This suggests some changes to developer 
behaviour, likely either as a deliberate effort by programmers seeking to avoid the perils of 
complicated dependency trees \cite{Kikas:2017}, or as a natural result of the ever-changing
ways in which JavaScript is used for project development. [ADD EXACT VALUES]

@@

As in the original paper we analyzed popularity of \code{npm} packages using three major measures
\begin{enumerate}
  \item The \textbf{\code{npm} rank} is calculated using the PageRank\cite{brin1998anatomy} of an \code{npm} package within a dependency graph that we built using the
    package metadata as described in Section \ref{Package Metadata}. PageRank is calculated for every package using a damping factor of 0.85 
    and stopping iterations once the cumulative change in values of vertices went below $10^{-6}$. We then order all packages by their PageRank to determine the
    \code{npm} rank, an relative ranking of package popularity with 1 being the most popular.
  \item \textbf{download rank}
\end{enumerate}

>>>>

\subsection{Package Metadata} \label{PackageMetadata}

@@

Figure \ref{packVSDependencies} presents the total number of \code{npm} packages over time, 
as well as the total number of package dependencies. Additionally, we have plotted
the average number of dependencies per \code{npm} package. Curiously, though total dependencies
continues to grow faster than the creation of new packages, the number of dependencies 
for the average package appears to be plateauing. If this trend continues, it could suggest
that the \code{npm} ecosystem is reaching some sort of equilibrium with regards to the number
of package dependencies.

To better visualize the status of inter-package dependencies, we constructed
a directed dependency graph using dependants as out-degrees and
dependencies as in-degrees. Based on this data, Figure \ref{outDegree}
displays the percentage of packages with various amounts of dependencies. 
This confirms some of our earlier suspicious: while the average number of dependencies 
of packages continues to increase, the percentage of packages with zero 
to three dependencies has actually increased since the end of the original paper's
reporting period \cite{Wittern:2016}. This supports the hypothesis that developer 
behaviour is changing, likely either as a deliberate effort by programmers seeking to avoid the perils of 
complicated dependency trees \cite{Kikas:2017}, or as a natural result of the ever-changing
ways in which JavaScript is used for project development. [ADD EXACT VALUES]

@@

As in the original paper we analyzed popularity of \code{npm} packages using three major measures
\begin{enumerate}
  \item The \textbf{\code{npm} rank} is calculated using the PageRank\cite{brin1998anatomy} of an \code{npm} package within a dependency graph that we built using the
    package metadata as described in Section \ref{PackageMetadata}. PageRank is calculated for every package using a damping factor of 0.85 
    and stopping iterations once the cumulative change in values of vertices went below $10^{-6}$. We then order all packages by their PageRank to determine the
    \code{npm} rank, an relative ranking of package popularity with 1 being the most popular.
  \item The \textbf{download rank} is based on the the gross volume of package downloads from the \code{npm}
    registry, then ordered relatively with 1 being the most downloaded.
  \item \textbf{\code{GitHub} rank} is a measure of the popularity of package use in public \code{GitHub} projects.
    This rank is created from a list of \code{npm} dependency occurrences found in \code{package.json} files, with rank 1
    meaning that the package was the most common dependency among analyzed \code{GitHub} repositories.  
\end{enumerate}
